Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
setpoints.

Transition between, and operation in, these different stages is
implemented as a simple state machine, summarized in
Table~\ref{tab:cs_tasks}. The main job of the state machine is to
adjust the reference signals to accomplish each task. In the
following, $r_X$ and $r_Y$ refer to the references for the
$X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis
setpoints during scanning and retraction, respectively.

>>>>

Transition between, and operation in, these different stages is
implemented as a simple state machine, summarized in
Table~\ref{tab:cs_tasks}. The main job of the state machine is to
adjust the reference signals to accomplish each task. In the
following, $r_X$ and $r_Y$, $r_Z$ refer to the references for the
$X$, $Y$, and $Z$ axes, respectively. The $Z$-axis setpoint $r_Z$
takes on values $r_{Z,s}$ (the scanning setpoint) and $\rzup$ (the
retraction setpoint).
